DTOADQ

### 2017-11-29 testdocs/_region_.tex
whatever

  $\alpha_{s|t}^{L|E}$ is the final radiance of either the emitter or eye path,
  and thus it is recursive in nature. That is, the value of $\alpha_i$ is
  dependent on $\alpha_{i-1}$, unless $i = 0$ in which case is the radiance of
  either the emitter or the eye path. This is shown below.
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      \frac{L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | \frac{W^0_e(z_0)}{p_A(z_0)},
      &i = 1,\\
      (\frac{f_s(y_{i+1} \rightarrow y_i \rightarrow y_{i-1})}{p_{\sigma}(y_i
      \rightarrow y_{i-1})} | \frac{f_s(z_{i-1} \rightarrow z_{i-2} \rightarrow
      z_{i-3}}{p_\sigma(z_{i-2} \rightarrow z_{i-1})}) \alpha^{L|E}_{i-1},
      &i > 1
    \end{cases}
  \end{align}
    For the case of $i = 0$, this would mean that the path does not exist. In
other words, forward or backward path tracing, the latter of which isn't
supported as camera lens are not defined in DTQ. Veach (and many other sources),
leave this in, but it's unnecessarily confusing. For $i = 1$, it is either a
point on the surface of a light, or the origin point on the 'delta eye'. The
connection strategy below describes how to connect the edges of the two paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 1,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s > 0, t > 1
    \end{cases}
  \end{align}
    Is the $s = 0, t > 1$ strategy worthwhile to compute? Those familiar with
next event estimation would know that there are situations in which this is
beneficial. Take, for example, a glossy surface with a small solid angle
subtending to the surface of a large light source. The $s=1$ sample strategy in
this case would only contribute when the $L0$ vertex is within that solid angle.
The effective strategy to sample in this case is $s = 0$. In code,
$\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

    Another question to consider is if the path should be able to reflect on the
light source. While under real circumstances, this is allowed, the contribution
is negligible and dismissed in DTOADQ. Also, there are no cases for $s = s, t =
0|1$ as the lens does not have a physical existence in the SDF map. The $t = 0$
case, where a photon from the light source hits the lens directly, is rather
pointless anyways, as a path generated by light-tracing would have to be able to
contribute to any pixel, which is not feasible on a GPU. The case of $t = 1$,
where the light path is connected to a position on the lens, is important for
effects such as depth of field and aperture. The only problem is due to time
constraints, this has not been implemented yet.

    One immediately obvious optimization that could be made with this model is
in regards to the visibility check in the geometric term, if you were to expand
$I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be cancelled out
for the entire equation, except for the connection term $c$. This is intuitive
as the paths $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ had
just been generated via raymarching. Specifically, the definition of $V$ is
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
    where $m$ is a march through the SDF map. A visibility check is only
necessary for the connection edge
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 

@@

of the sphere, and not its origin. \\$p_A^E(x_0 \rightarrow x_1)$ doesn't exist,
as there is no physical lens on the scene. [TODO - this might cahnge later]. One
of the benefits of this, is that there are no special cases for pathes where $t
= 0$, which is impossible to handle on the GPU as the path could contribute to
any arbitrary pixel [directly hitting the lens].

@@

  [Henyey]
   Diffuse Radation in the Galaxy, 1942. L, G. Henyey and J. L. Greenstein. 
\end{document}
\message{ !name(test.tex) !offset(-684) }

>>>>

  $\alpha_{s|t}^{L|E}$ is the final radiance of either the emitter or eye path,
  and thus it is recursive in nature. That is, the value of $\alpha_i$ is
  dependent on $\alpha_{i-1}$, unless $i = 0$ in which case is the radiance of
  either the emitter or the eye path. However, this can be simplified further,
because of Helmhotz reciprocity, BRDFs return the same value if $wo$ and $wi$
are switched. This is also the reason why forward and backward path tracing
work.
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      1.0 &i = 0,\\
      \frac{
      L_e^0(V_0 \rightarrow V_1)}{p_A(V_1)} | 1.0 &i = 1,\\
      \frac{f_s(V_0 \rightarrow V_1 \rightarrow V_2)}{p_{\sigma}(V_0
      \rightarrow V_1)} &i > 1
    \end{cases}
  \end{align}
    For the case of $i = 0$, this would mean that the path does not exist. In
other words, forward or backward path tracing, the latter of which isn't
supported as camera lens are not defined in DTQ. For $i = 1$, it is either a
point on the surface of a light, or the origin point on the 'delta eye'. Lastly,
the BRDF is used to calculate the albedo of each primitive in the scene, and is
then divided by the PDF sigma, which is the probability density of $v_i
\rightarrow v_{i-1}$. $\alpha_1^L$ is shown below:

\begin{lstlisting}
  float3 N      = Sample_Cosine_Sphere(si, &pdf_pos),
         origin = light.origin + light.radius*N,
         dir    = Reorient_Angle(Sample_Cosine_Hemisphere(si, &pdf_dir), N);
  float pdf_pos = 1.0f/(2.0f*TAU*SQR(light.radius)),
        pdf_amt = 1.0f/EMITTER_AMT;
  pv->irradiance = light.emission/(pdf_pos*pdf_amt*pdf_fwd);
\end{lstlisting}

  Note that the irradiance is being calculated in this case, that is, the amount
  of flux arriving at point $pv$. Though in the case of $s=1$, this is more like
  the radiance. The irradiance at $t > 1$ and $s > 1$ is shown:

\begin{lstlisting}
  float3 sample_dir, sample_f;
  float sample_pdf;
  _BSDF_Sample(wi, N, vtx, &sample_dir, &sample_pdf, &sample_f, si);
  *irradiance = sample_f * (*irradiance) * fabs(dot(N, sample_dir))/sample_pdf;
\end{lstlisting}

  The connection strategy below describes how to connect the edges of the two
paths. There is no $t = 0$ case as no physical camera lens exists on the scene.
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(L0 \rightarrow L1), &s = 0, t > 1,\\
      f_s(L0 \rightarrow L1 \rightarrow L2) G(E1 \leftrightarrow
      L1) f_s(L1 \rightarrow E1 \rightarrow E0), &s > 0, t > 1
    \end{cases}
  \end{align}
  In code:
  \begin{lstlisting}
Spectrum contribution = E1.irradiance * L1->irradiance;

// As there is no T=1 case, L1 -> E1 -> E0 [Le in s=1 case] must happen
contribution *= Subpath_Connection(L1, &E1, &E0);

// For s == 1, L1 = L0, a point on the surface of emitter, there is no
// L0 -> L1 -> E1 connection
if ( light_depth > 0 ) {
  // Connect L0 -> L1 -> E1
  contribution *= Subpath_Connection( L0,  L1, &E1);
}

// Geometric connection term [includes visibility check]
contribution *= Geometric_Term(&E1, L1, si, Tx);

    Is the $s = 0, t > 1$ strategy worthwhile to compute? Those familiar with
next event estimation would know that there are situations in which this is
beneficial. Take, for example, a glossy surface with a small solid angle
subtending to the surface of a large light source. The $s=1$ sample strategy in
this case would only contribute when the $L0$ vertex is within that solid angle.
The effective strategy to sample in this case is $s = 0$. In code,
$\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

    Another question to consider is if the path should be able to reflect on the
light source. While under real circumstances, this is allowed, the contribution
is negligible and dismissed in DTOADQ. Also, there are no cases for $s = s, t =
0|1$ as the lens does not have a physical existence in the SDF map. The $t = 0$
case, where a photon from the light source hits the lens directly, is rather
pointless anyways, as a path generated by light-tracing would have to be able to
contribute to any pixel, which is not feasible on a GPU.

@@

    of the sphere, and not its origin. For the eye:

@@

  [Henyey]
   Diffuse Radation in the Galaxy, 1942. L, G. Henyey and J. L. Greenstein. 
\end{document}
\message{ !name(test.tex) !offset(-707) }

### 2017-11-29 testdocs/test.tex
whatever

  $\alpha_{s|t}^{L|E}$ is the final radiance of either the emitter or eye path,
  and thus it is recursive in nature. That is, the value of $\alpha_i$ is
  dependent on $\alpha_{i-1}$, unless $i = 0$ in which case is the radiance of
  either the emitter or the eye path. However, this can be simplified further,
because of Helmhotz reciprocity, BRDFs return the same value if $wo$ and $wi$
are switched. This is also the reason why forward and backward path tracing
work.
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      1.0 &i = 0,\\
      \frac{
      L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | 1.0 &i = 1,\\
      \frac{f_s(v_{i-1} \rightarrow v_i \rightarrow v_{i+1})}{p_{\sigma}(v_i
      \rightarrow v_{i-1})} &i > 1
    \end{cases}
  \end{align}
    For the case of $i = 0$, this would mean that the path does not exist. In
other words, forward or backward path tracing, the latter of which isn't
supported as camera lens are not defined in DTQ. For $i = 1$, it is either a
point on the surface of a light, or the origin point on the 'delta eye'. Lastly,
the BRDF is used to calculate the albedo of each primitive in the scene, and is
then divided by the PDF sigma, which is the probability density of $v_i
\rightarrow v_{i-1}$. $\alpha_1^L$ is shown below:

@@

  The connection strategy below describes how to connect the edges of the two
paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 1,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s > 0, t > 1
    \end{cases}
  \end{align}
    Is the $s = 0, t > 1$ strategy worthwhile to compute? Those familiar with
next event estimation would know that there are situations in which this is
beneficial. Take, for example, a glossy surface with a small solid angle
subtending to the surface of a large light source. The $s=1$ sample strategy in
this case would only contribute when the $L0$ vertex is within that solid angle.
The effective strategy to sample in this case is $s = 0$. In code,
$\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

    Another question to consider is if the path should be able to reflect on the
light source. While under real circumstances, this is allowed, the contribution
is negligible and dismissed in DTOADQ. Also, there are no cases for $s = s, t =
0|1$ as the lens does not have a physical existence in the SDF map. The $t = 0$
case, where a photon from the light source hits the lens directly, is rather
pointless anyways, as a path generated by light-tracing would have to be able to
contribute to any pixel, which is not feasible on a GPU. The case of $t = 1$,
where the light path is connected to a position on the lens, is important for
effects such as depth of field and aperture. The only problem is due to time
constraints, this has not been implemented yet.

    One immediately obvious optimization that could be made with this model is
in regards to the visibility check in the geometric term, if you were to expand
$I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be cancelled out
for the entire equation, except for the connection term $c$. This is intuitive
as the paths $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ had
just been generated via raymarching. Specifically, the definition of $V$ is
  \begin{align}
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
  \end{align}
    where $m$ is a march through the SDF map. A visibility check is only
necessary for the connection edge
    \begin{align*}
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 
    \end{align*}
\\
    Moving on, for $\alpha^{L|E}_i$, these are equivalent for both $L$ and $E$,
the problem is that the $\bar{y}$ path is generated in perspective of the light
source, so there has to be a bit of caution in terms of perspective in when
generating the PDFs. $p_A$ is the PDF w.r.t. area, for the light path; we only
need to take the PDF of the solid angle of a sphere
  \begin{align}
    p_A^L(y_0 \rightarrow y_1) = p_{\sigma}^L(y_0 \rightarrow y_1) G(v
    \leftrightarrow \dot{v})\\
    p_{\sigma}^L(y_0 \rightarrow y_1) = \frac{1.0f}{\tau * (1.0f -
    \sqrt{\frac{R^2}{|y_0 - y_1|^2}})}
  \end{align}
    where $R$ is the radius of the sphere, note $y_0$ is a point on the surface
of the sphere, and not its origin. \\$p_A^E(x_0 \rightarrow x_1)$ doesn't exist,
as there is no physical lens on the scene. [TODO - this might cahnge later]. One
of the benefits of this, is that there are no special cases for pathes where $t
= 0$, which is impossible to handle on the GPU as the path could contribute to
any arbitrary pixel [directly hitting the lens].
  \begin{align}
    P_A^E = 1.0f
  \end{align}
    The $L^0_e$ is contribution from the light source. As of right now, DTOADQ
only supports area lights, so $L^0_e$ is set a constant for the emitter's
spectrum value. The $W_e^0$ is contribution from the eye source, that is, the
lens. Since the lens does not exist in the scene, as of now [TODO - this might
change later], there is no $W_e^0$. While this should be implemented in the
future, a hidden benefit of the current model is that there are no special cases
for paths where $t = 0$, which is impossible to handle on the GPU as any such
path could contribute to any arbitrary pixel [the light path is, after all,
directly hitting the lens]. So this has now become:
  \begin{align}
    \alpha_i^E = \Sigma_{i\leq 0} 
  \end{align}
  The amount that each path contributes to F differ greatly, so naively weighing
each contribution uniformly by something like 1.0f, or even, by inverse path
length, will producy very noisy images, and would not be worth the additional
computation time that BDPT requires, as shown below. To calculate the PDF of In
order to get good samples from the contributions, they must be combined in an
optimal manner using Multiple Importance Sampling: each contribution is weighted
by the PDF of the entire path itself:
  \begin{align*}
    F &\equiv \Sigma_s\Sigma_tW_{s, t}C_{s, t}\\
    C_{s, t} &= \alpha^L_s c_{s, t} \alpha^E_t
  \end{align*}
    where $W_{s, t}$ is the MIS weight of path $\bar{y} \leftarrow \bar{z}$, and
$C_{s, t}$ is the unweighted contribution of the same path. For clarity,
$C^U_{s, t}$ as described below is the unweighted contribution of the
    algorithm:
  \begin{align}
    C^u_{s, t} = (\alpha^L_s c_{s, t} \alpha^E_t) \equiv
    \frac{f_j(\bar{v})}{p(\bar{v})}
  \end{align}
  thus
  \begin{align}
    F = \Sigma_s\Sigma_tW_{s, t}C^u_{s, t}
  \end{align}
    The formula for Multiple Importance Sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
generated, while the denominator is the path density of other connection
strategies that could could have, in theory,$^{[1]}$ created the path. The
straight forward implementation of this has a lot of problems gone unresolved in
Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses and describe these
problems. Primarily, $P_i(\bar{x})$ will overflow CLFloat (due to the distance
in the Geometric term), and the straight forward implementation is very long,
hard to debug, and has a poor time complexity. But the important part is the end
result of their solution:
  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}
    However, DTOADQ can simplify a bit further; unlike above, there are two
paths for which to evaluate. Specifically, in the above term, for where $i < s$,
we have $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$,
which is the light path (i is iterating towards light-length s). The eye
contribution is inversed from this, (also iterating towards s, hence why
$\bar{x}_{i-1}$ is used). Another way of saying it, is $\bar{x} = \bar{y} ||
\bar{z}_{rev}$. In DTOADQ's case, the weights are calculated in the same
direction relative to its originator; in this case the perspective of the eye
path.
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And then the expanded form of $\mathcal{W}_i(\bar{x})$ looks like
  \begin{align}
    \mathcal{W}_i(\bar{x}) = \Pi_{n=2}^i(\frac{\overleftarrow
    {p_{\sigma}}(x_n)\overleftarrow {G}(x_n)}
    {\overrightarrow{p_{\sigma}}(x_n)\overrightarrow{G}(x_n)})
    * \frac{\overleftarrow{p_A}(x_1)}{\overrightarrow{p_A}(x_1)}
  \end{align}
    And now the MIS looks like:
  \begin{align}
    MIS_{s, t}(\bar{y}, \bar{z}) =
    \frac{1.0f}{\mathcal{W}_s(\bar{y}) + \mathcal{W}_t(\bar{z}) + 1.0f}
  \end{align}
    Thus, the final rendering equation for DTOADQ looks like such:
  \begin{align}
    P = \frac{1.0f}{N} \Sigma_{0}^{N} \Sigma_{s \le 0} \Sigma_{t \le 0}
    \alpha^L_s c_{s,t} \alpha^E_t MIS_{s, t}(\bar{y}, \bar{z})
  \end{align}

>>>>

  $\alpha_{s|t}^{L|E}$ is the final radiance of either the emitter or eye path,
  and thus it is recursive in nature. That is, the value of $\alpha_i$ is
  dependent on $\alpha_{i-1}$, unless $i = 0$ in which case is the radiance of
  either the emitter or the eye path. However, this can be simplified further,
because of Helmhotz reciprocity, BRDFs return the same value if $wo$ and $wi$
are switched. This is also the reason why forward and backward path tracing
work.
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      1.0 &i = 0,\\
      \frac{
      L_e^0(V_0 \rightarrow V_1)}{p_A(V_1)} | 1.0 &i = 1,\\
      \frac{f_s(V_0 \rightarrow V_1 \rightarrow V_2)}{p_{\sigma}(V_0
      \rightarrow V_1)} &i > 1
    \end{cases}
  \end{align}
    For the case of $i = 0$, this would mean that the path does not exist. In
other words, forward or backward path tracing, the latter of which isn't
supported as camera lens are not defined in DTQ. For $i = 1$, it is either a
point on the surface of a light, or the origin point on the 'delta eye'. Lastly,
the BRDF is used to calculate the albedo of each primitive in the scene, and is
then divided by the PDF sigma, which is the probability density of $v_i
\rightarrow v_{i-1}$. $\alpha_1^L$ is shown below:

@@

  The connection strategy below describes how to connect the edges of the two
paths. There is no $t = 0$ case as no physical camera lens exists on the scene.
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(L_0 \rightarrow L_1), &s = 0, t > 1,\\
      f_s(L_0 \rightarrow L_1 \rightarrow L2) G(E_1 \leftrightarrow
      L_1) f_s(L_1 \rightarrow E_1 \rightarrow E_0), &s > 0, t > 1
    \end{cases}
  \end{align}
  In code:
  \begin{lstlisting}
Spectrum contribution = E1.irradiance * L1->irradiance;

// As there is no T=1 case, L1 -> E1 -> E0 [Le in s=1 case] must happen
contribution *= Subpath_Connection(L1, &E1, &E0);

// For s == 1, L1 = L0, a point on the surface of emitter, there is no
// L0 -> L1 -> E1 connection
if ( light_depth > 0 ) {
  // Connect L0 -> L1 -> E1
  contribution *= Subpath_Connection( L0,  L1, &E1);
}

// Geometric connection term [includes visibility check]
contribution *= Geometric_Term(&E1, L1, si, Tx);

    Is the $s = 0, t > 1$ strategy worthwhile to compute? Those familiar with
next event estimation would know that there are situations in which this is
beneficial. Take, for example, a glossy surface with a small solid angle
subtending to the surface of a large light source. The $s=1$ sample strategy in
this case would only contribute when the $L0$ vertex is within that solid angle.
The effective strategy to sample in this case is $s = 0$. In code,
$\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

    Another question to consider is if the path should be able to reflect on the
light source. While under real circumstances, this is allowed, the contribution
is negligible and dismissed in DTOADQ. Also, there are no cases for $s = s, t =
0|1$ as the lens does not have a physical existence in the SDF map. The $t = 0$
case, where a photon from the light source hits the lens directly, is rather
pointless anyways, as a path generated by light-tracing would have to be able to
contribute to any pixel, which is not feasible on a GPU.
\\

The amount that each path contributes differ greatly, so naively weighing
each contribution uniformly by something like 1.0f, or even, by inverse path
length, will producy very noisy images, and would not be worth the additional
computation time that BDPT requires. Thus, as mentioned earlier, probability
distributions of the entire path are taken into account in order to generate
multiple importance samples.
    The formula for multiple importance sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
generated, while the denominator is the path density of other connection
strategies that could could have, in theory, created the path. The
straight forward implementation of this has a lot of problems gone unresolved in
Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses and describe these
problems. Primarily, $P_i(\bar{x})$ will overflow CLFloat (due to the distance
in the Geometric term), and the straight forward implementation is very long,
hard to debug, and has a poor time complexity. But the important part is the end
result of their solution:
  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}
    However, DTOADQ can simplify a bit further; unlike above, there are two
paths for which to evaluate. Specifically, in the above term, for where $i < s$,
we have $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$,
which is the light path (i is iterating towards light-length s). The eye
contribution is inversed from this, (also iterating towards s, hence why
$\bar{x}_{i-1}$ is used). . In DTOADQ's case, the weights are calculated in the
same direction relative to its originator; in this case the perspective of the
eye path. Not only this, but unlike any implementation I've found of BDPT, I
don't recalculate each path's probability and MIS every vertex. That is, usually
on calculating MIS for each connection, the MIS and probability values are
recalculated for each vertex in the path. As this is not possible given that
only the light-path exists in memory, an array for MIS/probability is stored
corresponding to each light vertex, and a single MIS/probability is stored
corresponding to $E_1$. Thus, the weight on each path looks like:
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And then the expanded form of $\mathcal{W}_i(\bar{x})$ looks like
  \begin{align}
    \mathcal{W}_i(\bar{x}) = \Pi_{n=2}^i(\frac{\overleftarrow
    {p_{\sigma}}(x_n)\overleftarrow {G}(x_n)}
    {\overrightarrow{p_{\sigma}}(x_n)\overrightarrow{G}(x_n)})
    * \frac{\overleftarrow{p_A}(x_1)}{\overrightarrow{p_A}(x_1)}
  \end{align}
    And now the MIS looks like:
  \begin{align}
    MIS_{s, t}(\bar{y}, \bar{z}) =
    \frac{1.0f}{\mathcal{W}_s(\bar{y}) + \mathcal{W}_t(\bar{z}) + 1.0f}
  \end{align}
    Thus, the final rendering equation for DTOADQ looks like such:
  \begin{align}
    P = \frac{1.0f}{N} \Sigma_{0}^{N} \Sigma_{s \le 0} \Sigma_{t \le 0}
    \alpha^L_s c_{s,t} \alpha^E_t MIS_{s, t}(\bar{y}, \bar{z})
  \end{align}
